Self Regulation Ontology Retest Data Report

### 2017-10-31 code/SRO_Report.Rmd
added function to get variance breakdowns

@@

```{r}
rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
                     icc = rep(NA, length(numeric_cols)), 
                     eta_sq = rep(NA, length(numeric_cols)),
                     sem = rep(NA, length(numeric_cols)))

@@

for(i in 1:length(numeric_cols)){
  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
  rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
}

>>>>

get_var_breakdown <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', sample='full', sample_vec){
  if(sample=='full'){
    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
  }
  else if(sample=='bootstrap'){
    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide', sample='bootstrap', sample_vec = sample_vec)
  }

  df = df %>% select(-dv, -sub_id)
  icc = ICC(df)
  var_breakdown = data.frame(subs = ICC(tmp)$summary[[1]][1,'Mean Sq'],
                             ind = ICC(tmp)$summary[[1]][2,'Mean Sq'],
                             resid = ICC(tmp)$summary[[1]][3,'Mean Sq'])
  return(var_breakdown)
  }

@@

```{r}
rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
                     icc = rep(NA, length(numeric_cols)), 
                     eta_sq = rep(NA, length(numeric_cols)),
                     sem = rep(NA, length(numeric_cols)),
                     var_subs = rep(NA, length(numeric_cols)),
                     var_ind = rep(NA, length(numeric_cols)),
                     var_resid = rep(NA, length(numeric_cols)))

@@

for(i in 1:length(numeric_cols)){
  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
  rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$subs
  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$ind
  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$resid
}
